Confirmation of \srcfull{} as a long period radio transient

### 2025-05-19 paper/main.tex
Added words to final missing sections: data availability, abstract.

% Abstract of the paper
\begin{abstract}
\dots
\end{abstract}

@@

No significant polarised emission was detected in the MWA pulses, as well as the 2023 MeerKAT pulses.
The apparent lack of polarisation in the MeerKAT data set is likely due to low S/N coupled with the source not being not being centred in the beam.
Much more careful analysis would be needed to obtain reliable limits on the polarised components of those pulses.

@@

\dots

>>>>

% Abstract of the paper
\begin{abstract}
We report the discovery of several new pulses from the source \srcfull{} (\src{}), confirming it as a long period transient (LPT) with a period of ${\sim}1.16\,$hours. The pulses are significantly scattered, consistent with Galactic electron density models. Two of the new pulses also had measurable polarisation, but unlike the originally detected pulse, the polarisation angle does not behave as expected from the rotating vector model. We interpret historical non-detections of \src{} as an intrinsic intermittency that occurs on month-long timescales, and discuss possible causes. We conjecture that, like other LPTs with periods $\gtrsim 1\,$hour, \src{} is a white-dwarf binary pulsar, but note that its period is marginally shorter than the minimum known polar orbital period.
\end{abstract}

@@

No significant polarised emission was detected in the MWA pulses, as well as the 2023 MeerKAT pulses.
The apparent lack of polarisation in the MeerKAT data set is likely due to low S/N coupled with the source not being not being centred in the beam.
Much more careful imaging analysis would be needed to obtain reliable measurements or limits on the polarised components of those pulses.

@@

The raw visibilities for the MWA, ASKAP, and MeerKAT data sets are available via the respective telescopes' data portals. 
The post-imaged dynamic spectra, analyses, and timing analysis data products (ToAs, pulse properties) are publicly available on GitHub\footnote{TODO: Make this available upon publication.}.
